A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-12-17 paper/paper.tex
paper: some more polish

\begin{definition}[$\DeltaPlus$]
  The definition of $\DeltaPlus$ is shown below. Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
  \begin{align*}
    \Obj_{\DeltaPlus}       & := \Nat                                                                             \\
    \Hom_{\DeltaPlus}(p, n) & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
    g \circ f               & :=
    \begin{cases}
      f                  & \text{if $g = \epsilon$}                                                        \\
      0\,(g' \circ f)  & \text{if $g = (0\,g')$}                                                 \\
      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a = 0$ or $\kstar$} \\
    \end{cases}                \\
    \id                     & := \kstar \ldots \kstar \text{ $n$ times for $\id \in \Hom_{\DeltaPlus}(n, n)$}
  \end{align*}
\end{definition}

@@

  \begin{align*}
    \Obj_{\Cube}       & := \Nat                                                                          \\
    \Hom_{\Cube}(p, n) & := \{l \in \{L, R, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
    g \circ f          & :=
    \begin{cases}
      f                  & \text{if $g = \epsilon$}                                                               \\
      a\,(g' \circ f)  & \text{if $g = (a\,g')$}, \text{where $a = L$ or $R$}                           \\
      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a = L$, $R$, or $\kstar$} \\
    \end{cases} \\
    \id                & := \kstar \ldots \kstar \text{ $n$ times}
  \end{align*}

@@

\begin{definition}[$\hexagon$]
  The definition of $\nu$-semi-shape category is shown below. Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
  \begin{align*}
    \Obj_{\hexagon}       & := \Nat                                                                           \\
    \Hom_{\hexagon}(p, n) & := \{l \in (\nu \sqcup \{\kstar\})^n \mid \text{number of $\kstar$ in $l = p$}\}    \\
    g \circ f             & :=
    \begin{cases}
      f                  & \text{if $g = \epsilon$}                                                                 \\
      a\,(g' \circ f)  & \text{if $g = (a\,g')$}, \text{where $a \in \nu$}                                \\
      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a \in \nu$ or $a = \kstar$} \\
    \end{cases}   \\
    \id                   & := \kstar \ldots \kstar \text{ $n$ times for $\id \in \Hom_{\hexagon}(n, n)$}
  \end{align*}
\end{definition}

>>>>

\begin{definition}[$\DeltaPlus$]
  The definition of $\DeltaPlus$ is shown below. Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
  \begin{align*}
    \Obj_{\DeltaPlus}       & := \Nat                                                                             \\
    \Hom_{\DeltaPlus}(p, n) & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
    g \circ f               & :=
    \begin{cases}
      f                  & \text{if $g = \epsilon$}                                                        \\
      0\,(g' \circ f)  & \text{if $g = 0\,g'$}                                                 \\
      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a = 0$ or $\kstar$} \\
    \end{cases}                \\
    \id                     & := \kstar \ldots \kstar \text{ $n$ times for $\id \in \Hom_{\DeltaPlus}(n, n)$}
  \end{align*}
\end{definition}

@@

  \begin{align*}
    \Obj_{\Cube}       & := \Nat                                                                          \\
    \Hom_{\Cube}(p, n) & := \{l \in \{L, R, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
    g \circ f          & :=
    \begin{cases}
      f                  & \text{if $g = \epsilon$}                                                               \\
      a\,(g' \circ f)  & \text{if $g = a\,g'$}, \text{where $a = L$ or $R$}                           \\
      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a = L$, $R$, or $\kstar$} \\
    \end{cases} \\
    \id                & := \kstar \ldots \kstar \text{ $n$ times}
  \end{align*}

@@

\begin{definition}[$\hexagon$]
  The definition of $\nu$-semi-shape category is shown below. Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
  \begin{align*}
    \Obj_{\hexagon}       & := \Nat                                                                           \\
    \Hom_{\hexagon}(p, n) & := \{l \in (\nu \sqcup \{\kstar\})^n \mid \text{number of $\kstar$ in $l = p$}\}    \\
    g \circ f             & :=
    \begin{cases}
      f                  & \text{if $g = \epsilon$}                                                                 \\
      a\,(g' \circ f)  & \text{if $g = a\,g'$}, \text{where $a \in \nu$}                                \\
      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a \in \nu$ or $a = \kstar$} \\
    \end{cases}   \\
    \id                   & := \kstar \ldots \kstar \text{ $n$ times for $\id \in \Hom_{\hexagon}(n, n)$}
  \end{align*}
\end{definition}
